# Signal processing methodology


``` {r filter-design, include=FALSE, echo=FALSE}
# Bandpass filter design
bw <- butter(n = 2, w = Wpass, type = "pass",  plane = "z", output = "Arma")
bw_freq_resp <- freqz(bw, fs = fs_rec)
names(bw_freq_resp) <- str_replace(string = names(bw_freq_resp), pattern = "w", replacement = "f")
```

Since TLM simulation results will consist of sound pressure signals at each receiver for a given noise source type and valid until the frequency *f*~max~ set to `r f_pass_max` Hz, the signal processing methodology applied to the experimental signals consists in extracting the audio samples corresponding to each measurement configuration, namely:

* for each sequence (*seq*) from 1 to `r nb_seqs`,
* for each source-receiver distance from `r paste(df_timeline$distance[c(1, nrow(df_timeline))], "m", sep = " ", collapse = " to ")`,
* for each noise type (`r (paste(gsub(".", " ", noise_types, fixed = TRUE), collapse = ", "))`).

Then, a Butterworth passband filter of order `r filt_order` is designed for the bandwidth [`r paste(filt_fpass, "Hz", sep = " ", collapse = "; ")`] and convolved with each experimental raw signal sample to remove frequencies not modelled by the TLM model.

``` {r filter-test-init, include=FALSE, echo=FALSE, fig.cap = "Illustration of the passband filtering applied to a generated white noise signal.", out.width = '100%', fig.align = 'center', results = 'asis', dev = 'png'}
# Generate white noise
len_sig_test <- 5000  # Length of signal
wn_gen_filename <- paste0("./output/", "generated_white_noise.wav")  # Name of the generated audio file for the test noise
wn_filtered_filename <- str_replace(string = wn_gen_filename, pattern = "generated", replacement = "filtered")
# Time axis
axe_t <- seq(0, len_sig_test-1) / fs_rec
# Time signal
time_raw_wav <- gen_white_noise(sig_len = len_sig_test, f_samp = fs_rec, out_wav_filename = wn_gen_filename)
time_raw_sig <- time_raw_wav@left / 2^(time_raw_wav@bit-1)
time_raw_sig <- time_raw_sig / max(c(min(time_raw_sig), max(time_raw_sig))) # Normalize signal between -1 and 1
# Bandpass filtering
time_filtered_sig <- filtfilt(filt = bw, x = time_raw_sig)
time_filtered_wav <- savewav(wave = bwfilter(wave = time_raw_wav, f = fs_rec, channel = 1, n = filt_order, bandpass = TRUE, from = filt_fpass[1], to = filt_fpass[2], listen = FALSE, output = "matrix"), f = fs_rec, channel = 1, filename = paste0("./output/", "filtered_white_noise.wav"))
# Dataframe of time signals
time_sigs_df <- data.frame(axe_t, time_raw_sig, time_filtered_sig)
# Dataframe of spectra
axe_f = fs_rec * seq(0, (length(time_raw_sig)/2)) / length(time_raw_sig)
fft_raw_sig <- fft(time_raw_sig) / length(time_raw_sig)
freq_raw_sig2 <- abs(fft_raw_sig/ length(time_raw_sig))  # two-sided spectrum
freq_raw_sig <- freq_raw_sig2[seq(1, length(time_raw_sig)/2 + 1)]  # single-sided spectrum
fft_filtered_sig <- fft(time_filtered_sig) / length(time_filtered_sig)
freq_filtered_sig2 <- abs(fft_filtered_sig/ length(time_filtered_sig))  # two-sided spectrum
freq_filtered_sig <- freq_filtered_sig2[seq(1, length(time_filtered_sig)/2 + 1)]  # single-sided spectrum
freq_sigs_df <- data.frame(axe_f, freq_raw_sig, freq_filtered_sig)
```

The figure \@ref(fig:filter-test-plot) illustrates the signal processing methodology for a white noise of `r paste(round(x = len_sig_test / fs_rec, digits = 1), "s", sep = " ")` generated thanks to the *noisew* function of the *seewave* R library.

``` {r filter-test-plot, include=TRUE, echo=FALSE, fig.cap = paste0("Illustration of the passband filtering applied to a generated white noise signal of ", round(x = len_sig_test / fs_rec, digits = 1), " s sampled at ", fs_rec, " Hz: (top) raw white noise and (bottom) passband filtered white noise."), out.width = '100%', fig.align = 'center', results = 'asis', dev = 'png'}
# Plot raw time signal
t_plt_raw <- ggplot(data = time_sigs_df, aes(x = axe_t, y = time_raw_sig)) +
  geom_line(aes(y = time_raw_sig, colour = "Raw signal", group = 1,
                text = paste("<b><br>Time: </br>", sprintf("%0.5f", axe_t), " s</b>",
                             "<b><br>Sound pressure: </br>", sprintf('%.2e', time_raw_sig), " Pa</b>")),
            colour = "red") +
    labs(x = "Time (s)", y = "Sound pressure (Pa)") +
  theme(plot.title = element_text(hjust = 0.5))

# Plot bandpass filtered time signal
t_plt_filt <- ggplot(data = time_sigs_df, aes(x = axe_t, y = time_filtered_sig)) +
    geom_line(aes(y = time_raw_sig, colour = "Clean signal", group = 1,
                  text = paste("<b><br>Time: </br>", sprintf("%0.5f", axe_t), " s</b>",
                               "<b><br>Sound pressure: </br>", sprintf('%.2e', time_filtered_sig), " Pa</b>")),
            colour = "blue") +
  labs(x = "Time (s)", y = "Sound pressure (Pa)") +
  theme(plot.title = element_text(hjust = 0.5))

# Plot spectrum of the raw time signal
f_plt_raw <- ggplot(data = freq_sigs_df, aes(x = axe_f, y = freq_raw_sig)) +
    geom_line(aes(y = freq_raw_sig, colour = " signal", group = 1,
                  text = paste("<b><br>Frequency: </br>", sprintf("%0.5f", axe_f), " Hz</b>",
                               "<b><br>|Y(f)|: </br>", sprintf('%.2e', freq_raw_sig), "</b>")),
            colour = "red") +
    labs(x = "Frequency (Hz)", y = "|Y(f)|") + 
  ggtitle(" ")

## Plot spectrum of the filtered time signal
# f_plt_filt <- ggplot(data = freq_sigs_df, aes(x = axe_f, y = freq_filtered_sig)) +
#     geom_line(aes(y = freq_filtered_sig, colour = "Clean signal", group = 1,
#                   text = paste("<b><br>Frequency: </br>", sprintf("%0.5f", axe_f), " Hz</b>",
#                                "<b><br>|Y(f)|: </br>", sprintf('%.2e', freq_filtered_sig), "</b>")),
#             colour = "blue") +
#     labs(x = "Frequency (Hz)", y = "|Y(f)|")

max_length <- max(c(length(freq_sigs_df$axe_f), length(bw_freq_resp$f)))
freq_sigs_df2 <- data.frame(axe_f_sig = c(freq_sigs_df$axe_f, rep(NA, max_length - length(freq_sigs_df$axe_f))), 
                 freq_filtered_sig = c(freq_sigs_df$freq_filtered_sig, rep(NA, max_length - length(freq_sigs_df$freq_filtered_sig))), 
                 axe_f_bw = c(bw_freq_resp$f, rep(NA, max_length - length(bw_freq_resp$f))), 
                 mag_bw = c(abs(bw_freq_resp$h), rep(NA, max_length - length(bw_freq_resp$h))))
                 # mag_bw = c(20 * log10(abs(bw_freq_resp$h)), rep(NA, max_length - length(bw_freq_resp$f))))

scale <- max(is.finite(freq_sigs_df2$mag_bw), na.rm = TRUE) / max(abs(freq_sigs_df2$freq_filtered_sig), na.rm = TRUE)

# Plot spectrum of the filtered time signal and of the bandpass filter
f_plt_filt <- ggplot(data = freq_sigs_df2, aes(x = axe_f_sig)) +
  geom_line(aes(x = axe_f_sig, y = freq_filtered_sig, colour = "Filtered signal", group = 1, 
                text = paste("<b><br>Frequency: </br>", sprintf("%0.5f", axe_f_sig), " Hz</b>",
                             "<b><br>|Y(f)|: </br>", sprintf('%.2e', freq_filtered_sig), "</b>")), 
            colour = "blue") +
  geom_line(aes(x = axe_f_bw, y = mag_bw / scale, colour = "Butterworth filter", group = 1, 
                text = paste("<b><br>Frequency: </br>", sprintf("%0.5f", axe_f_bw), " Hz</b>",
                             "<b><br>|Y(f)|: </br>", sprintf('%.2e', mag_bw), "</b>")), 
            colour = "green") + 
  geom_vline(geom="label", xintercept = filt_fpass, linetype="dashed", color = "violet", linewidth = 1) +
  annotate(geom = "text", x = filt_fpass, y = -Inf, label = filt_fpass, size = 3, color = "violet", lineheight = .1, hjust = .05, vjust = .5, angle = 90) + 
  coord_cartesian(clip = "off") + 
  scale_y_continuous(name = "|Y(f)|",  # Features of the first axis
                     limits = c(min(freq_filtered_sig), max(freq_filtered_sig)), 
                     sec.axis = sec_axis(~.*scale, name="Magnitude (dB)")) +  # Features of the second axis
  labs(x = "Frequency (Hz)")

# Remove legends
t_plt_raw <- t_plt_raw + theme(legend.position="none")
t_plt_filt <- t_plt_filt + theme(legend.position="none")
f_plt_raw <- f_plt_raw + theme(legend.position="none")
f_plt_filt <- f_plt_filt + theme(legend.position="none")

# Create of a list with the plots
sigs_plts <- list(t_plt_raw, t_plt_filt, f_plt_raw, f_plt_filt)

# Create row and column titles
col.titles = c("Time signal", "Spectrum")
row.titles = c("Raw signal", "Filtered signal")

sigs_plts[1:2] = lapply(1:2, function(i) arrangeGrob(sigs_plts[[i]], left=row.titles[i]))

# grid.arrange(t_plt_raw, f_plt_raw, t_plt_filt, f_plt_filt, nrow=2, ncol=2)
grid.arrange(grobs=lapply(c(1,3), function(i) {
  arrangeGrob(grobs=sigs_plts[i:(i+1)], top=col.titles[i/2 + 1], ncol=1)
}), ncol=2)
```


```{r init-audio-player, include=FALSE, echo=FALSE}
audio_path  <- "./output"
audio_files <- list.files(audio_path, 
                          pattern = "\\.wav$",
                          recursive = FALSE,
                          all.files = FALSE,
                          full.names = TRUE)
```

::: {}
::: {.column width="10%"}
:::
::: {.column width="40%"}
```{r play-generated-white-noise, include=TRUE, echo=FALSE}
player_audio(wav_filename = audio_files[str_detect(string = audio_files, pattern = "generated")], player_title = "Play generated white noise signal.")
```
:::
::: {.column width="5%"}
:::
::: {.column width="40%"}
```{r play-filtered-white-noise, include=TRUE, echo=FALSE}
player_audio(wav_filename = audio_files[str_detect(string = audio_files, pattern = "filtered")], player_title = "Play filtered white noise signal.")
```
:::
::: {.column width="5%"}
:::
:::