```{r get-seq-infos-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-{{ids-1}}, echo=FALSE, include=FALSE}
seq_dist_colname <- c(colnames(df_samples)[[{{ids}}]], 
                      colnames(df_samples)[[{{ids+1}}]], 
                      colnames(df_samples)[[{{ids+2}}]], 
                      colnames(df_samples)[[{{ids+3}}]])
parts <- str_split(string = seq_dist_colname[1], pattern = "_")[[1]]
seq_name <- parts[1]
seq_id <- str_remove(string = seq_name, pattern = "seq")
dist_name <- parts[2]
rep_name <- parts[3]
rep_id <- as.integer(str_remove(string = rep_name, pattern = "rep"))
noise_name <- str_replace(string = noise_type, pattern = "_", replacement = " ")
nb_reps <- length(t.beg)
```

`r if(dist_name == "0.5m") {paste0("## Sequence ", seq_id)}`

`r paste0("### Distance: ", dist_name)`

::: {}
::: {.column width="48%"}
```{r raw-time-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-plots-{{ids-1}}, include=TRUE, echo=FALSE}
seq_reps_id <- seq({{ids}}-1, {{ids}}+2)
raw_time_plots <- lapply(seq_reps_id,
                         function(seq_rep_id) knitr::knit_expand(file = "Plot_raw_time_df.Rmd"))
```
`r knit(text = unlist(raw_time_plots))`

:::
::: {.column width="2%"}
:::
::: {.column width="48%"}
```{r raw-freq-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-plots-{{ids-1}}, include=TRUE, echo=FALSE}
raw_freq_plots <- lapply(seq({{ids}}-1, {{ids}}+2), 
                         function(seq_rep_id) knitr::knit_expand(file = "Plot_raw_spec_df.Rmd"))
```
`r knit(text = unlist(raw_freq_plots))`
:::
:::


::: {}
::: {.column width="48%"}
```{r raw-audio-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-{{ids-1}}, include=TRUE, echo=FALSE}
idr <- rep_id
raw_audios <- lapply({{ids-1}}, function(seq_rep_id) knitr::knit_expand(file = "Audio_raw_sample.Rmd"))
```
`r knit(text = unlist(raw_audios))`

:::
::: {.column width="2%"}
:::
::: {.column width="48%"}
```{r raw-audio-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-{{ids}}, include=TRUE, echo=FALSE}
idr <- rep_id+1
raw_audios <- lapply({{ids}}, function(seq_rep_id) knitr::knit_expand(file = "Audio_raw_sample.Rmd"))
```
`r knit(text = unlist(raw_audios))`
:::
:::

::: {}
::: {.column width="48%"}
```{r raw-audio-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-{{ids+1}}, include=TRUE, echo=FALSE}
idr <- rep_id+2
raw_audios <- lapply({{ids+1}}, function(seq_rep_id) knitr::knit_expand(file = "Audio_raw_sample.Rmd"))
```
`r knit(text = unlist(raw_audios))`

:::
::: {.column width="2%"}
:::
::: {.column width="48%"}
```{r raw-audio-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-{{ids+2}}, include=TRUE, echo=FALSE}
idr <- rep_id+3
raw_audios <- lapply({{ids+2}}, function(seq_rep_id) knitr::knit_expand(file = "Audio_raw_sample.Rmd"))
```
`r knit(text = unlist(raw_audios))`
:::
:::

::: {}
::: {.column width="48%"}
```{r filt-time-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-plots-{{ids-1}}, include=TRUE, echo=FALSE}
filt_time_plots <- lapply(seq({{ids}}-1, {{ids}}+2), 
                         function(seq_rep_id) knitr::knit_expand(file = "Plot_filt_time_df.Rmd"))
```
`r knit(text = unlist(filt_time_plots))`

:::
::: {.column width="2%"}
:::
::: {.column width="48%"}
```{r filt-freq-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-plots-{{ids-1}}, include=TRUE, echo=FALSE}
filt_freq_plots <- lapply(seq({{ids}}-1, {{ids}}+2), 
                         function(seq_rep_id) knitr::knit_expand(file = "Plot_filt_spec_df.Rmd"))
```
`r knit(text = unlist(filt_freq_plots))`
:::
:::


::: {}
::: {.column width="48%"}
```{r filt-audio-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-{{ids-1}}, include=TRUE, echo=FALSE}
idr <- rep_id
raw_audios <- lapply({{ids-1}}, function(seq_rep_id) knitr::knit_expand(file = "Audio_filt_sample.Rmd"))
```
`r knit(text = unlist(raw_audios))`

:::
::: {.column width="2%"}
:::
::: {.column width="48%"}
```{r filt-audio-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-{{ids}}, include=TRUE, echo=FALSE}
idr <- rep_id+1
raw_audios <- lapply({{ids}}, function(seq_rep_id) knitr::knit_expand(file = "Audio_filt_sample.Rmd"))
```
`r knit(text = unlist(raw_audios))`
:::
:::

::: {}
::: {.column width="48%"}
```{r filt-audio-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-{{ids+1}}, include=TRUE, echo=FALSE}
idr <- rep_id+2
raw_audios <- lapply({{ids+1}}, function(seq_rep_id) knitr::knit_expand(file = "Audio_filt_sample.Rmd"))
```
`r knit(text = unlist(raw_audios))`

:::
::: {.column width="2%"}
:::
::: {.column width="48%"}
```{r filt-audio-sample-{{str_replace(string = noise_type, pattern = "_", replacement = "-")}}-{{ids+2}}, include=TRUE, echo=FALSE}
idr <- rep_id+3
raw_audios <- lapply({{ids+2}}, function(seq_rep_id) knitr::knit_expand(file = "Audio_filt_sample.Rmd"))
```
`r knit(text = unlist(raw_audios))`
:::
:::

